Network Configuration Synthesis with Abstract Topologies

### 2016-11-10 paper/abstraction/appendix.tex
updating appendix with new definitions

We define syntax for an abstraction of BGP configurations -- called ABGP -- in Figure~\ref{fig:abgp-syntax}. An ABGP policy consists of a map from topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of prefix (templates) $t$ and their corresponding prefix configuration $pc$. A prefix configuration $pc$ is a sequence of match actions $ma$. Each match action $ma$ consists of a preference value $n_1$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $n_2$, as well as export neighbors $ns_2$ and the updated community value $n_3$.

\vspace{2em}
\begin{figure}[h!]\small

  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3) & \textit{match action} \\
     ps   &::=& \{ t_1, ~\dots,~ t_k \} & \textit{predicates} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
  \end{array} \]%

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \textbf{compile}_\textbf{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k) ) = \\
     ~~~~~ \{ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(V), \\
     ~~~~~~~~~ rc = \bigcup_i~ \{ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ in = \{ b ~\vert~ (b,q_n) \in \text{adjIn}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) \} \} \\
     \\
     \textbf{compile}( p_1, \dots, p_k ) = \\
     ~~~~~~ compile_{ABGP}(compile_{PG}(p_1), \dots, compile_{PG}(p_k)) \\
  \end{array} \]%

  \end{minipage}

  \vspace{1em}
  \hrulefill%
  \vspace{1em}

  \caption{BGP syntax and compilation.}
  \label{fig:abgp-syntax}
\end{figure}%

@@

Figure~\ref{fig:abgp-syntax} also defines compilation from a \sysname policy to an ABGP policy. It starts by compiling separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$, the particular test $t_i$, and the preference ordering $ord_i$.

The function $compile_{ABGP}$ then takes tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy. It looks at each incoming neighbor with the same community state $q_n$ and matches any of those neighbor with the preference provided by the ordering $ord$ obtained from the search for local preferences. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.

We assume a particular router $l$ appears at most once in any abgp specification.
We often build configs using set-builder notation.  For instance,
$\{l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc)\}$ denotes the abgp policy

\[ \begin{array}{c}
  l_1 \rightarrow rc_{11},... \\
  ...           \\
  l_k \rightarrow rc_{1k},... \\
\end{array} \]

where $l_1, ..., l_k$ are the nodes in the topology
and each $rc_{ij}$ satisfies $p(l_i,rc_{ij})$.

@@

We define what it means to concretize an abstract \sysname policy. 
Concretization takes as input, a policy and a context $\Gamma$ mapping from a template prefix to a set of pairs of a concrete prefix and a concrete location where the prefix is owned.

\[ \begin{array}{lcl}
  con(\emptyset,\Gamma,f)                        & = & \emptyset \\
  con(l,\Gamma,f)                                & = & \Sigma ~ f^{-1}(l) \\
  con(r_1 \cup r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cup con(r_2,\Gamma,f) \\
  con(r_1 \cap r_2,\Gamma,f)                     & = & con(r_1,\Gamma,f) \cap con(r_2,\Gamma,f) \\
  con(!r,\Gamma,f)                               & = & !con(r,\Gamma,f) \\
  con(r^*,\Gamma,f)                              & = & con(r,\Gamma,f)^* \\
  con(pfx \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & pfx \Rightarrow con(r_1,\Gamma,f), \dots, con(r_k,\Gamma,f) \\
  con(\$x \Rightarrow r_1, \dots, r_k,\Gamma,f)  & = & 
       \{ pfx \Rightarrow con(r_1,\Gamma,f) \cap \text{end}(l), 
          \dots, 
          con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x) \} \\
  %& & ~~~~~~~~~~~~~~~ \dots, \\
  %& & ~~~~~~~~~~~~~~~ con(r_k,\Gamma,G) \cap \text{end}(l) ~\vert~ (pfx,l) \in \Gamma(x),  ~l \in G.V \} \\
  con(p_1, \dots, p_n, \Gamma, f)                & = & con(p_1,\Gamma,f), \dots, con(p_n,\Gamma,f) \\
\end{array} \]

For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete values under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that traffic is owned by the concrete location $l$. \textbf{Note}: we need the side condition that $\text{end}(l) \cap con(r_i,\Gamma) \neq \emptyset$ if $con(r_i,\Gamma) \neq \emptyset$.
We can also define concretization over the ABGP policy as:

\[ \begin{array}{lcl}
     con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G) 
        & = & 
        \{ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) \}
        \\
     con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G) 
        & = &  
        con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     con(pfx \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        pfx \rightarrow con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     con(\$x \rightarrow {pc},\ell,\Gamma,f,G) 
        & = &  
        \{ pfx \rightarrow con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (pfx, l) \in \Gamma(x) \}
        \\
     con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G) 
        & = &
        con(ma_1,o,\ell,\Gamma,f,G), \dots, con(ma_k,o,\ell,\Gamma,f,G)
        \\

     con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G) 
        & = & \textbf{if}~ ns_1 = \{G.s\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (con({ns}_2,\ell,\Gamma,f,G),n_3)

        \\
     con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G) 
        & = &  
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
\end{array} \]

We use the symbol $\bullet$ to denote that a particular value in a sequence is removed from the sequence.

@@

The goal of this section is to prove that the concretization and compilation functions commute: 
$$con(compile(pol),\Gamma,f,G) = compile(con(pol,\Gamma,f))$$ 
That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete. Note that the theorem states that the resulting ABGP policies are actually syntactically equivalent and not semantically equivalent. First we need a few helper theorems about compilation.

@@

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma ~ f^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup f^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by homomorphism} & & \\
  \end{array} \]

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup_B~ \{ b \in f^{-1}(B), (b,\ell) \in G.E, (B,q_N) \in \text{adjIn}(PG^A,M) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup_C~ \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ \{ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ in = \bigcup \{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m) \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \bigcup \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) \} \\
  \end{array} \]%

>>>>

\newcommand{\Con}{\text{con}}
\newcommand{\Pfx}{\mathit{pfx}}%

\vspace{2em}
\begin{figure*}[t!]\small%

  \hrulefill%

  \vspace{1em}%
  \begin{minipage}[t]{.46\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     d    &   & & \textit{integer} \\
     c    &   & & \textit{community} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     ma   &::=& d : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\%
  \end{array} \]%%

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
     \\
     \text{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
  \end{array} \]%
  \end{minipage}%

  \vspace{1em}
  \vspace{1em}%

  \vspace*{-2\baselineskip}
  \begin{minipage}[t]{1.01\linewidth}
  \hdr{Policy Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(\emptyset, \Gamma, f)      &=& \emptyset \\
     \Con(l, \Gamma, f)              &=& \Sigma_i ~ f_i^{-1}(l) \\
     \Con(r_1 \cup r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cup \Con(r_2,\Gamma,f) \\
     \Con(r_1 \cap r_2, \Gamma, f)   &=& \Con(r_1,\Gamma,f) \cap \Con(r_2,\Gamma,f) \\
     \Con(!r, \Gamma, f)             &=& !\Con(r,\Gamma,f) \\
     \Con(r^*, \Gamma, f)            &=& \Con(r,\Gamma,f)^* \\%
     \Con(\Pfx ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&
          \Pfx ~\Path~ \Con(r_1,\Gamma,f), ~\dots~, \Con(r_k,\Gamma,f)  \\%
     \Con(\$x ~\Path~ r_1, ~\dots~, r_k, \Gamma, f) &=&%
         [~ \Pfx ~\Path~ \Con(r_1,\Gamma,f) \cap \text{end}(l), ~\dots~, \\%
         & & ~~~~~~~~~~~~~~~ \Con(r_k,\Gamma,f) \cap \text{end}(l) ~\vert~ (\Pfx,l) \in \Gamma(x) ~]  \\%
     \Con(p_1, \dots, p_n, \Gamma,f) &=& \Con(p_1, \Gamma,f), \dots, \Con(p_n, \Gamma,f) \\%

  \end{array} \]%
  \end{minipage}%

  \vspace{1em}
  \vspace{1em}%

  \begin{minipage}[t]{\linewidth}
  \hdr{ABGP Concretization}{}
  \vspace*{-2\baselineskip}
  %
  \[ \begin{array}{lcl}
     \\
     \Con(l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k,\Gamma,f,G)
        & = &
        \mathit{append}_i~ [~ \ell \rightarrow con(rc_i,\ell,\Gamma,f,G)  ~\vert~ \ell \in f^{-1}(l_i) ~]
        \\
     \Con(t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        & = &
        \Con(t_1 \rightarrow {pc}_1,\ell,\Gamma,f,G), \dots, \Con(t_k \rightarrow {pc}_k,\ell,\Gamma,f,G)
        \\
     \Con(\Pfx \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        \Pfx \rightarrow \Con(pc,\text{true},\ell,\Gamma,f,G)
        \\
     \Con(\$x \rightarrow {pc},\ell,\Gamma,f,G)
        & = &
        [~ \Pfx \rightarrow \Con(pc, l=\ell, \ell,\Gamma,f,G) ~\vert~ (\Pfx, l) \in \Gamma(x) ~]
        \\
     \Con(ma_1, \dots, ma_k,o,\ell,\Gamma,f,G)
        & = &
        \Con(ma_1,o,\ell,\Gamma,f,G), \dots, \Con(ma_k,o,\ell,\Gamma,f,G)
        \\%
     \Con(n_1 : ({ns}_1, n_2) \rightarrow ({ns}_2, n_3),o,\ell,\Gamma,f,G)
        & = & \textbf{if}~ ns_1 = \{\text{start}\} ~\text{and}~ o = \text{false} ~\textbf{then}~ \bullet \\
        &   & \textbf{else}~ n_1 : ( \Con({ns}_1,\ell,\Gamma,f,G), n_2) \rightarrow (\Con({ns}_2,\ell,\Gamma,f,G),n_3)%

        \\
     \Con(\{ l_1, ~\dots,~ l_k \}, \ell, \Gamma,f,G)
        & = &
        \bigcup_i ~ \{ x ~\vert~ x \in f^{-1}(l_i),~ (x,\ell) \in G.E \}
        \\
  \end{array} \]%
  \end{minipage}%

  \vspace{1em}
  \hrulefill%
  \vspace{1em}%

  \caption{ABGP syntax, compilation from product graphs, policy concretization, and ABGP concretization.}
  \label{fig:concretization}
\end{figure*}%

\para{ABGP language}

We introduct a simple language for BGP configurations called ABGP. Figure~\ref{fig:concretization} shows the syntax for an ABGP policy. An ABGP policy maps topology locations $l$ to router configurations $rc$. Each router configuration $rc$ is a sequence of predicates $t$ and their corresponding configuration $pc$. A prefix configuration $pc$ is a sequence of match actions. Each match action $ma$ consists of a preference value $d$, followed by a set of imports from neighbors $ns_1$ and community value (\IE, state of the product graph) $c_1$ expected from those neighbors, as well as export neighbors $ns_2$ and the community value $c_2$ to attach before sending to those neighbors.%

@@

Figure~\ref{fig:concretization} defines compilation from a \sysname policy to an ABGP policy. It starts by compiling ($\text{compile}_\text{PG}$) separately each constraint of the form $p_i = (t_i ~\Path~ r_{i1} ~\Prefer~ r_{ik})$ to a product graph $PG = (G', s, P)$. The function $\text{compile}_\text{PG}$ returns the test $t_i$, product graph $PG_i$, and the preference ordering $ord_i$.
%
The function $\text{compile}_\text{ABGP}$ then takes a sequence of tuples $(t_i, PG_i, ord_i)$ and returns an ABGP policy. For each internal router, it looks at each set of neighbor with the same community state $q_n$ and matches any of those neighbors with the preference provided by the ordering $ord$. It then exports this advertisement to each adjacent peer along an outgoing edge and adds the community value for the current state $q_m$.%

We assume a particular router $l$ appears at most once in any abgp specification.
We build configs using list-comprehension notation. For instance,
$[~ l \rightarrow rc ~\vert~ l \in V \wedge p(l,rc) ~]$ denotes the abgp policy
%
\[ \begin{array}{c}
  l_1 \rightarrow rc_{1},... \\
  ...           \\
  l_k \rightarrow rc_{k},... \\
\end{array} \]

where $l_1, ..., l_k$ are the nodes in the topology
and each $rc_{i}$ satisfies $p(l_i,rc_{i})$. We also use the $\mathit{append}$ operator to denote sequence concatenation.%

@@

Concretization for a \sysname policy takes as input, the policy and a context
$\Gamma : Var \rightarrow 2^{Prefix \times V}$,
which maps from a template prefix to a set of pairs of a concrete prefix and a concrete location that "owns" the prefix.
%
For each regular expression $r$, we replace each abstract location with the sum over its corresponding concrete locations under the inverse homomorphism $f^{-1}$. For each template variable, we replace it with a new entry for each of its corresponding concrete prefixes under the supplied mapping $\Gamma$. We also intersect the resulting concretized regular expression with $\text{end}(l)$ to capture the fact that this traffic is owned by the concrete location $l$.%

We also define concretization over the ABGP policy in a similar manner. We replace each abstract router configuration $l \rightarrow rc$ a new entry for each concrete location $\ell \in f^{-1}(l)$. The concrete location $\ell$ is passed as a parameter to $con$ to remember the current router.
%
To concretize a prefix policy with a template ($\$x \rightarrow pc$) we replace it with a sequence of policies, one for each prefix in context ($(pfx,l) \in \Gamma(x)$). Match action statements where the set of import neighbors is the singleton set containing the product graph start node $\{ start \}$ and we are not currently at looking at the router configuration for the location specified in the context $l$, then we drop the match action. This is denoted with the $\bullet$ symbol. Finally, to concretize a set of neighbors, we again use $f^{-1}$ to find the set of concrete neighbors under the inverse homomorphism, but then restrict it to those that are actually connected in the underlying concrete topology with $G.E$.

@@

The goal of this section is to prove that the concretization and compilation functions commute: 
$$con(compile(pol,G^A),\Gamma,f,G) = compile(con(pol,\Gamma,f), G)$$ 
That is -- we can perform compilation directly over the abstraction and only substitute for the concrete values on after compilation is complete. Note that the theorem states that the resulting ABGP policies are actually syntactically equivalent and not semantically equivalent. First we need a few helper theorems about compilation.

@@

\emph{Case $l$:}
  \[ \begin{array}{lll}
    p \in \Lang(con(l,\Gamma,f)) &\iff& f(p) \in \Lang(l) \\
    p \in \Lang(\Sigma_i ~ f_i^{-1}(l)) &\iff& f(p) \in \Lang(l) \\
    p \in \bigcup_i f_i^{-1}(l) &\iff& f(p) \in \Lang(l) \\
    p \in f^{-1}(l) &\iff& f(p) \in \{ l \} \\
    p \in f^{-1}(l) &\iff& f(p) = l \\
    \text{by homomorphism} & & \\
  \end{array} \]

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(\{b\in f^{-1}(B), (b,\ell) \in G.E, B \in BS\},q_N) ~\vert~ (\_,q_N) \in I, BS=\{B~\vert~ (B,q_N) \in I \} \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in I\} \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%
